\documentclass{article}

% Redefine \maketitle command
\makeatletter
\renewcommand{\maketitle}{%
  \begin{center}
    {\Large\@title\par} % Title size can be adjusted here
    \vspace{0em} % Adjust vertical space between title and author
    {\large\begin{tabular}[t]{c}\@author\end{tabular}}
  \end{center}
}
\makeatother

\usepackage[utf8]{inputenc}
\usepackage[left=1.25in,right=1.25in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\thispagestyle{empty}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\lhead{Alan Mendoza Sosa / Curriculum Vitae / 2025}
\rhead{\thepage}


\title{CURRICULUM VITAE}

\begin{document}
\begin{flushleft}
\maketitle

\subsection*{Alan Mendoza Sosa}
\texttt{}{alan.mendozasosa@yale.edu}

\subsection*{Education}
\vspace{1pt}\hrule\vspace{0pt}
\begin{itemize}[align=left, leftmargin=.73in,parsep=1pt]
\setstretch{.25}
\setlength{\itemindent}{-.57in}
    \item[] PhD  \hspace{.5cm} \textbf{Yale University}, Spanish, expected graduation: 2027
    \vspace{1em}  
        
    \item[] MPhil \hspace{.24cm} \textbf{University of Cambridge}, European, Latin American, and Comparative Literatures and Cultures, 2021
    \vspace{3pt}    
    \item[] \hspace{1.31cm} Master's Thesis: \textit{Decolonial Challenges: Indigeneity in Recent Cultural Production from Mexico (2017-2019)}. Advisor: Prof. Carlos Fonseca.
    \vspace{1em}
    
    \item[] BA \hspace{.68cm} \textbf{Brown University}, Comparative Literature, 2020
    \vspace{.3em}
    \item[] \hspace{1.31cm} Honors Thesis: \textit{Queer Sor Juana? Power Relations in Love Poems by Sor Juana Inés de la Cruz and Two Contemporary Novels}. Advisor: Prof. Stephanie Merrim.
\end{itemize}

\subsection*{Honors and Awards}
\vspace{1pt}\hrule\vspace{0pt}
\begin{itemize}[leftmargin=*,parsep=1pt]
    \item[] 2026 \hspace{.5cm} Associates in Teaching Fellowship
    \item[] 2026 \hspace{.5cm} MacMillan Center International Conference Travel Grant
    \item[] 2025 \hspace{.5cm} Dean's Fund for Colloquia and Symposia Award
    \item[] 2025 \hspace{.5cm} Yale's Graduate Student Assembly Conference Travel Award
    \item[] 2025 \hspace{.5cm} MacMillan Center International Conference Travel Grant
    \item[] 2024 \hspace{.5cm} Center for Language Studies Graduate Fellowship
    \vspace{2pt}
    \item[] 2024 \hspace{.5cm} MacMillan Center International Conference Travel Grant
    \vspace{2pt}
    \item[] 2023 \hspace{.5cm} Yale's LGBT Studies Funds for Lesbian and Gay Studies Research Award
    \vspace{2pt}
    \item[] 2023 \hspace{.5cm} Yale's Whitney Humanities Center Grant for Research Working Group
    \vspace{2pt}
    \item[] 2022 \hspace{.5cm} Professional Experience Fellowship at Council on Latin American and Iberian Studies
    \vspace{2pt}
    \item[] 2022 \hspace{.5cm} Yale's Franke Fellowship for Outstanding Graduate Applicants
    \vspace{2pt}
    \item[] 2020 \hspace{.5cm} Conacyt-FINBA Mexican National Scholarship for Graduate Study Abroad
    \vspace{2pt}
    \item[] 2020 \hspace{.5cm} Brown's CareerLab SPRINT Award for Student-Faculty Collaboration
    \vspace{2pt}
    \item[] 2019 \hspace{.5cm} Brown's Undergraduate Teaching and Research Award
    \vspace{2pt}
    \item[] 2019 \hspace{.5cm} John Hay Library's Undergraduate Research Fellowship
    \vspace{2pt}
    \item[] 2019 \hspace{.5cm} Brown's Fellowship for Research in Caribbean and Latin American Studies
    \vspace{2pt}
    \item[] 2016 \hspace{.5cm} EducationUSA Opportunity Funds Scholarship for Study Abroad
        
\end{itemize}


\subsection*{Publications}
\vspace{1pt}
\hrule
\vspace{0pt}
\subsubsection*{Journal Articles}
\setstretch{.25}
\begin{itemize}[align=left, leftmargin=*,parsep=1pt]
    \item[]```Un punto de la aurora'. Poética y epígrafe en Abigael Bohórquez.'' \textit{Connotas. Revista de crítica y teoría literarias}, no. 28, 2024, pp. 160-185. doi:10.36798/critlit.v0i28.490.
    \vspace{5pt}
    \item[]``Reimaginar la nación: Indigeneidad colonial en \textit{El laberinto de la soledad} y \textit{Estética de la penuria}." \textit{Humanística. Revista de estudios críticos y literarios}, no. 4, 2022, pp. 57-70.
\end{itemize}

\subsubsection*{Book Chapter}
\setstretch{.25}
\begin{itemize}[align=left, leftmargin=*,parsep=1pt]
    \item[]``El cuerpo contra el prejuicio. Optimismo militante y desautorización ideológica en la narrativa hispanounidense.'' \textit{Corporeidades en tránsito: narrativas corporales de la diferencia en la literatura Latinx escrita en español en los Estados Unidos}, edited by Etna Avalos, 2025.
\end{itemize}

\subsubsection*{Poetry}
\begin{itemize}[align=left, leftmargin=*,parsep=1pt]
\setstretch{.25}
    \vspace{5pt}
    \item[]``Incierto.''\textit{Río Grande Review}, UT El Paso, 2025.
    \vspace{5pt}
    \item[] ``Ambulante.''\textit{Variantes}, no. 1, Yale U, 2024.
    \vspace{5pt}
    \item[] ``Delta.''\textit{Buenos Aires Poetry}, no. 1 (new series), 2024.
    \vspace{5pt}
    \item[]``Poemas.''\textit{Punto en línea}, no. 111, 2024.
    \vspace{5pt}
    \item[]```[Sin título]' and `Ciclos*'.'' \textit{Fondo Editorial Tierra Adentro}, Pride Month Dossier, 2023.
    \vspace{5pt}
    \item[]\textit{La bestia que habito}. Herring Publishers, 2022.
    \vspace{5pt}
    \item[]``Ritual.'' \textit{Página Salmón}, no. 13, 2019.
    \vspace{5pt}
    \item[]``En las grietas del palacio soñábamos flores.'' \textit{Página Salmón}, no. 11, 2019.
\end{itemize}

\subsubsection*{Writing in Public Media}
\begin{itemize}[align=left, leftmargin=*,parsep=1pt]
\setstretch{.25}
    \item[]``Planting Modernity.'' \textit{RETROSPECTA}, no. 47, 2024, p. 287.
    \vspace{5pt}
    \item[]``Translation as Disorder in Carlos Fonseca’s \textit{Austral}.''\textit{Asymptote Journal}, 2023.
\end{itemize}

\subsubsection*{Translations}
\begin{itemize}[align=left, leftmargin=*,parsep=1pt]
\setstretch{.25}
    \item[]Hugh MacDiarmid. ``Poems.'' \textit{Buenos Aires Poetry}, no. 3, 2025.
    \vspace{5pt}
    \item[]Sayak Valencia and Liliana Falcón. ``Continuities and discontinuities between the concepts of feminicide and transfeminicide in Mexico.'' \textit{The Routledge International Handbook on Femicide and Feminicide}, edited by Myrna Dawson and Saide Mobayed Vega, Routledge, 2023, pp. 380-389.
    \vspace{5pt}
    \item[]Julia E. Monárrez Fragoso. ``Systemic Sexual Feminicide.'' \textit{The Routledge International Handbook on Femicide and Feminicide}, edited by Myrna Dawson and Saide Mobayed Vega, Routledge, 2023, pp. 321-331.
    \vspace{5pt}
    \item[]César Cañedo. ``La primera vez que corrí.'' \textit{Anuario de poesía de San Diego 2021: Pozol (Bilingual Edition)}, edited by Olga García, San Diego Entertainment and Arts Guild (SDEAG), 2022, pp. 24-25.
\end{itemize}

\subsection*{Teaching and Tutoring}
\vspace{1pt}\hrule\vspace{0pt}
\begin{itemize}[align=left, leftmargin=.73in,parsep=1pt]
\setstretch{.25}
\setlength{\itemindent}{-.57in}
    \item[] \textbf{Teaching Assistant} 
    \vspace{.1em}
    \item[] Yale University, New Haven, CT, 2024 - Present \hspace{.5cm}
    \item[] \hspace{1.3cm} - Assist course ``Radical Films of Latin America'' taught by Professor Moira Fradinger
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Direct 1 hour long weekly discussion section
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Comment and supervise students' weekly discussion posts, midterms, and finals
    \vspace{1em}
    
    \item[] \textbf{Graduate  Fellow at Center for Language Studies } 
    \vspace{.1em}
    \item[] Yale University, New Haven, CT, 2023 - Present \hspace{.5cm} 
    \item[] \hspace{1.3cm} - Co-direct semester-long workshop ``Fundamentals of Language Teaching'' aimed at introducing graduate language instructors to SLA pedagogy
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Contribute to the improvement and development of Center for Language Teaching
    \item[] \hspace{1.3cm} - Host weekly office hours for participants of CLS workshops
    \vspace{.1em}
    \vspace{1em}
    
    \item[] \textbf{Graduate Writing Fellow} 
    \vspace{.1em}
    \item[] Yale's Poorvu Center, New Haven, CT, 2022 - Present \hspace{.1em}
    \item[] \hspace{1.3cm} - Edit graduate and professional students' papers
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Direct one-on-one writing conferences with graduate and professional students
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Facilitate and supervise academic writing workshops
    \vspace{1em}
    
    \item[] \textbf{Summer Instructor for Yale Young Global Scholars } 
    \vspace{.1em}
    \item[] Yale University, New Haven, CT, 2024 \hspace{.5cm} 
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Taught seminars ``Powerful Words: Critiquing Imperialism in Latinx and Latin American Poetry'' and ``Existentialism'' for a total of 27 class hours
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Supervised and directed capstone projects
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Conducted room curfew checks and safety inspections in student dorms
    \vspace{1em}
   
    \item[] \textbf{Summer Instructor for Yale Young Global Scholars } 
    \vspace{.1em}
    \item[] Yale University, New Haven, CT, 2023 \hspace{.5cm} 
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Taught seminars ``Unruly Beasts: Cats in Fiction and Poetry'' and ``Existentialism'' for a total of 27 class hours
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Supervised and directed capstone projects
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Conducted room curfew checks and safety inspections in student dorms    
    \vspace{1em}
    
    \item[] \textbf{Humanities Professor} 
    \vspace{.1em}
    \item[] Arkansas State University Mexico, Queretaro, Mexico, 2021-2022 
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Taught classes ``Academic Writing in English'' and ``World Literature'' for two semesters 
    \vspace{.1em}
    \item[] \hspace{1.3cm} - Supervised undergraduate Writing Lab
\end{itemize}

\subsection*{Presentations}
\vspace{1pt}
\hrule
\vspace{0pt}

\begin{itemize}[align=left, leftmargin=*,parsep=1pt]
\setstretch{.25}
\item[]``Multihispanic Utopianism? Ethos, Aesthetics, and Politics of the ‘Las Yubartas’ Literary Award.'' Modern Language Association Annual Convention 2025.
    \vspace{5pt}
\item[]``Infancia y género en la literatura queer mexicana.'' Latin American Studies Association 2024.
    \vspace{5pt}
\item[]``Sounding the Earth: Ariel Guzik’s Decolonial Acoustemology.'' Graduate Conference \textit{A Laboratory of Worlds: Futures, Ruptures, Possibilities} 2023.
    \vspace{5pt}
\item[]``The Latinx Origins of Mexican Queer Literature.'' 14th Annual Harvard-Yale-Brown Graduate Conference in Book History 2023.
\end{itemize}

\subsection*{Relevant Experience}
\vspace{1pt}
\hrule
\vspace{0pt}
\begin{itemize}[align=left, leftmargin=*,parsep=1pt]
\setstretch{.25}
\item[] \textbf{Co-lead ``Queer Literature in Spanish'' working group} 
    \vspace{.1em}
    \item[] Yale University, New Haven, CT, 2023 - Present \hspace{.5cm} 
    \vspace{5pt}
    
\item[] \textbf{Co-hosted roundtable with Mexican novelist Yuri Herrera} 
    \vspace{.1em}
    \item[] Yale University, New Haven, CT, 2023 \hspace{.5cm} 
    \vspace{1em}
\end{itemize}

\end{flushleft}
\end{document}